\documentclass{article}

\usepackage{geometry}
\usepackage{makecell}
\usepackage{array}
\usepackage{multicol}
\usepackage[ngerman=ngerman-x-latest]{hyphsubst}
\usepackage{setspace}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\newcolumntype{?}{!{\vrule width 1pt}}
\renewcommand\theadalign{tl}
\setstretch{1.10}
\setlength{\parindent}{0pt}

\geometry{top=12mm, left=1cm, right=2cm}
\title{\vspace{-3cm}22W Fachkommunikation- und Translation}
\author{Andreas Hofer}

\begin{document}
	\section{Einheit 2}
	\subsection{Terminology}
	Terminology is important for translators as terminological competence is translator competence (Austermühl 2010:3). If you don't have familiarity with the specific terminology, then you are unable to communicate effectively. All kinds of communities can have very specialised terminology and accuracy in LSP is especially important. For example an incorrect term can lead to fatal consequences in a medical context, making the accuracy of every translation important. In addition communities expect specialised terminology to be accepted as professionals in a field. The terminological competence is thus a key component of being a competent translator.
	\subsubsection{Defining Terminology}
	What is terminology even? Terminology is: \textit{The set of all terms, standardised or not, belonging to a specific domain}. Bowker also defines terminology as \textit{Any lexical item that poses a challenge and must be researched.}
	The ISO is providing an international list of internationally agreed definitions of key terminology within a specifc field.
	\subsubsection{Concept and Designation}
	A concept is \textit{A unit of knowledge created by a unique combination of characteristics.} Which is not very descriptive. For example a democracy is the idea of a political community in which the people have sovereign power and there is a popular vote. \\
	Another example are migrants and refugees, which are often used interchangeably but have key differences between them.
	For example these two terms share the feature that they are leaving their home country for a relatively long time but the motivation might be very different.
	\textbf{Concepts and Designations:} \\
	Concepts are defined by designations. For example happiness can be defined through several means, for example a smile or an emoji or a specific sentence. Similarly red can be designated by a string of letters, but also by HEX codes or nonverbally with the colour. \\
	For this reason when translating you must find the concept in a language and then find the correct designation in the target language. \\
	Often identifying the corresponding designation is not a straightforward process. A TL and SL may have similar concepts, but they are not necessarily identical. Political offices are often not similar due to similar systems used in differne countries. \\
	Occasionally a TL might not even have a designation for specific concept like the \textit{Speaker of the House of Commons} in the UK.
	\subsubsection{Translation Strategies}
	When you get a new client you first have to find information about the client. A good starting point for terminology would be the client's website. Ideally there is a company glossary which one can use but it often does not exist. \\
	A survey form 2012 showed that a large amount of translators at that time still used mono- and bilingual dictionaries. These two can also be combined in order to find candidates for translating a concept and then checking the specific definition. Online dictionaries are also often superior to physical dictionaries since they tend to be more up-to-date. But care should be taken when using a dictionary that the defined designation does in fact have the correct context. It also works within LSPs where LSP specific terms might not be too useful to an excessive amount of LSP words.
	\textbf{Wikipedia} is also a good starting point for one's research, as it gives a good overview and a good way to find additional resources. But Wikipedia should not be used as a final source as the content is not necessarily (But nevertheless often) correct.\\
	\textbf{Google Searches} can also prove an invaluable tool when trying to find information with wildcard characters and advanced search options. \\
	\subsection{Translation Problems nach Christiane Nord}
	Christiane Nord has defined four major translation problems, each of which describe different problems in translating:
	\begin{itemize}
		\item{Pragmatic Problems}
		\begin{itemize}
			\item{Intertextual references (to other documents, laws or directives)}
			\item{Names, places, peopl,e historical events}
		\end{itemize}
		\item{Intercultural Problems}
		\begin{itemize}
			\item{Convention based problems. For example centimetres and inches but also texttype conventions. Brackets are for example far less common in English than in German}
		\end{itemize}
		\item{Interlingual Problems}
		\begin{itemize}
			\item{Domain specific terms (Verbs and nouns and compound nouns)}
			\item{Structural differences in vocabulary, syntax or grammar}
		\end{itemize}
		\item{Text Specific Problems}
		\begin{itemize}
			\item{Problems arising from combinations of aspects in a particular text}
		\end{itemize}
	\end{itemize}
	\section{Corpora}
	\subsection{What is a Corpus?}
	A corpus (From Latin \textit{corpus, corpora} for body) is a collection of texts. An example could be the Hippocratic corpus, which is the collection of texts authored by Hippocrates. In Humanities though corpus has a more narrow definition: \\
	A corpus should be a large collection of texts adhering to a specific standard.
	\subsubsection{How large should the corpus be?}
	A corpus should be large enough to find secific patterns within a genre. One occurence would not be enough. Qualitative analyses usually include 20 to 25 texts. In a quantitative analysis many more should be included (100+) \\
	In this context qualitative means that the analysis goes deeper than merely counting the number of occurences, as would be usually done in quantitative analyses. \\
	\subsubsection{What criteria?}
	A corpus is not a random collection of texts but a carefully curated one. Based on the purpose of the corpus, the criteria can be different. A starting point could be the domain, genre and text type.
	\subsubsection{What is a corpus?}
	Bowker and Pearson state, that texts in a corpus must be authentic, reliable and representative. \\
	\begin{itemize}
		\item{Authentic:}
		\begin{itemize}
			\item{Genuine communication instead of fabricated examples. A medical exchange from a TV-Show should not be used in a medical corpus.}
		\end{itemize}
		\item{Reliable:}
		\begin{itemize}
			\item{Texts should be from reliable sources. Blogs are often not considered reliable a as anybody can pen a blog.}
		\end{itemize}
		\item{Representative:}
		\begin{itemize}
			\item{Texts have to fit the convention of the specific text you need to ensure that they are relevant to the task.}
		\end{itemize}
	\end{itemize}

	\subsection{Why use a specialised corpus?}
	\begin{itemize}
		\item{Because terminology research is very time consuming.}
		\begin{itemize}
			\item{A study has shown that veteran translators use 25\% of their time with corpus analysis, while inexperiences translators use up to 60\%.}
		\end{itemize}
		\item{You can find collocations for common words much quicker.}
		\begin{itemize}
			\item{Coming back to a medical context it is easier to figure out which preposition to use for gene encoding.}
		\end{itemize}
		\item{You can do a quantitative analysis.}
		\begin{itemize}
			\item{You can figure out which term is more often used. When a term collocates with two words but one is used radically more often, you are wont to use the more common one.}
		\end{itemize}
	\end{itemize}

	There are general and specialised corpora. General corpora tend to have many many more words than specialised ones but are also less accurate for things you might need. For example the British National Corpus (BNC) has 100 million entries, while the Medical Web Corpus \textit{only} has 33 but all of them are related to the medical field.\\
	
	\section{Legal Language}
	Legal language is the language of the law and the language related to law. But what is the law? \\
	Law is a system of social conventions defined by social agreements and legislation that regulates the orderly living of people within their culture. For example road laws govern how you should behave while driving to ensure harmony between all parties. \\
	But we encounter legal texts very often in our daily lives without realising. Whenever we agree to a cookie disclaimer, we sign a legal contract. You also sign a legal contract when you start a lease for example. \\
	But legal language can also be found outside of this setting, with legal language being a fixed part in fiction used in crime novels among others. \\
	A good example for a legal text is a will. Wills follow a rigid structure and make use of multiple formulae, like often starting with \textit{This is the last will and testament of}. It can also be specific to a certain region, with the UK requiring two witnesses when it is signed. In Austria you do not require witnesses if you are writing it by hand. \\
	\subsection{English legal language}
	Legal language is extremely conservative, with register and legal archaisms being very slow to change. It also has a lot of conventional language. For example modal verbs are carefully chosen with each one having a specific meaning. \textit{Will} and \textit{shall} have a very different meaning, for example. \\
	Legal translation is so important because the exchange between countries only works if legal texts are understood by all parties. International organisations with differing languages can hardly cooperate if the legal texts associated with them are not translated precisely. They are also very sensitive, as the wording of a law can change what rights you have.\\
	It is also the largest subcategory of specialised translation, being larger than advertising or business translations. \\
	\subsection{Legal translation}
	There is no direct connection between legal languages and legal systems. For example the legal language is very different between English speaking countries, since the language may seem the same, it is bound to the law of the specific country. The same applies to, like French, in Canada, France or Switzerland. The conclusion to this is, that there is not universal legal system as a legal system is beholden to the social norms of a society. \\
	\subsection{Types of legal systems}
	There are two predominant types of legal systems:
	\begin{itemize}
		\item{The civil law}
		\begin{itemize}
			\item{All laws are codified that are continously expanded and updated. The courts only interpret the law based on a specific situation. The judge only establishes the facts and the case.}
		\end{itemize}
		\item{The common law}
		\begin{itemize}
			\item{Legislation is based on precedence and individual decisions, which were used as a justification for later decisions. It is generally uncoded law, and laws were just based on precedent at first.}
		\end{itemize}
		\item{It can be summed up by saying, that in civil law judges apply the law, while in common law judges make the law.}
	\end{itemize}
	\subsection{Challenges of legal systems}
	There is a particular challenge of translating between common and civil law legal systems. Some definitions do not exist in one legal system, while they do in the other.

	\section{Technical/Scientific/Medical Language}
	\textit{What is scientific translation even?} It is knowledge deriving from the osbervation and rational study of the natural world. This also means that this knowledge is, in our understanding, universal. Scientific translations thus involve situations where one must translate for the scientific community. \\
	\textit{Technical Language} on the other hand is language used in instruction manuals, among other things aimed at end users. There is also language by professionals for professionals like patent applications or documentation. \\
	\subsection{Properties of scientific language}
	\begin{itemize}
		\item{\textbf{Universal vs culture-bound}: Scientific language is more universal than, e.g. legal language, but there are still culture-bound expressions among other things that are different in different languages. For example \textit{Survival of the fittest} becomes \textit{The victory of the superior over the inferior} in Japanese. Thus, while the language may be the same, the framework in which it fits might be different.}
		\item{\textbf{Expert vs laypeople}: Technical-scientific language can be both aimed towards laypeople as well as experts. Information leaflets are aimed towards end-users, while other texts are solely aimed towards other scientists.}
		\item{\textbf{Fidelity vs functional adequacy}: Can the language be held as closely to the source text as possible or do you have to "foreignise" the text. Occasionally information that is relevant for one audience is irrelevant for another.}
		\item{\textbf{stable or unstable}: Does the language change quickly or does it stay the same. While science used to be relatively slow in its development, recently there have been a large amount of discoveries, which causes technical language to shift rapidly.}
	\end{itemize}

	\section{Business Language}
	Business English tends to be very concise and straigh to the point. Often there's no embellishments to shorten the sentences. In addition many acronyms are used. There's a number of domain specific terms for business language, which may look like LGP but have a very different meaning. \\
	Business English also likes using metaphors, often using weather or farming metaphors to make a point, which might not have direct translations since the target language does not use metaphors as extensively.
	

	

	

















	
\end{document}